My title

### 2024-03-18 paper/paper.qmd
Echo false working now:)

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(palmerpenguins)
```

@@

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

@@

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

@@

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
execute:
  echo: FALSE 
---

@@

library(tidyverse)
library(here)

```

@@

@@

@@

TESTING GROUND

```{r}
### Load required libraries
library(ggplot2)
library(tidyr)

```

```{r}

```

```{r,echo=FALSE, results=FALSE}
#| echo: false
#| warning: false
#| message: false

# Plot 1: GGPlot for GunLaw
Gunlaw <- read_csv(here("./data/analysis_data/Gunlaw.csv"))
transform(Gunlaw, 'Total Americans in Favour' = as.numeric('Total Americans in Favour'))

names(Gunlaw) <- c("Year", "Total")

ggplot(data=Gunlaw, aes(x = Year, y = Total, group = 1)) +
  geom_line()+
  labs(title = "Percentage of Americans in favour of police backed gun permits", y = "Total % of Americans in favour")

```
